\section{Devices Used}

For the purposes of evaluating the performance of both the scorer and the scorer
and parser, a Mac Pro (Early 2008 - MacPro3,1) was used. This was fitted with
two Intel Xeon E5462 processors, and a nVidia Tesla C2075 GPU. In addition,
there was a separate machine fitted with an Intel Xeon Phi 51100P. An AMD system
with a traditional CPU setup with 4x AMD Operon 6366 HE CPUs was also used. A
brief overview of the hardware will be given to provide some perspective to the
results which follow.

\subsection{Mac Pro System}

The Mac Pro was running Mac OS X version 10.8.5 (Build Version 12F45). Both the
nVidia and Intel OpenCL SDKs were installed and up to date at time of writing.

\begin{itemize}

\item[CPU] The motherboard has two CPU sockets, both with an Intel Xeon E5462
\footnote{\url{http://ark.intel.com/products/33084/Intel-Xeon-Processor-E5462
-12M-Cache-2_80-GHz-1600-MHz-FSB}} processor. This is a quad core processor with
a 2.8GHz clock speed and 12MB of Level 2 cache per processor.

\item[RAM] There is 14GB of PC2-6400 (800MHz) DDR2 RAM installed, with error
correcting code (ECC) enabled.

\item[GPU] The GPU is an nVidia Tesla C2075
\footnote{\url{http://www.nvidia.co.uk/docs/IO/43395/NV-DS-Tesla-C2075.pdf}}.
The device has 6GB of dedicated GDDR5 memory running at 1.5GHz giving an
internal memory bandwidth of 144GB/s. There are 448 ``CUDA Cores'' with a clock
frequency of 1.15GHz. It has been installed in a PCIe 1.0 slot with 16x lane
bandwidth giving a total theoretical bandwidth between its on-board memory and
main memory of 4GB/s (250MB/s per lane).

\end{itemize}

\subsection{Intel Xeon Phi System}

The system is running the SUSE Enterprise Server 11 Linux distribution. This
system was used solely for running the software system on the Intel Xeon Phi and
did not have a graphics card fitted.

\begin{itemize}

\item[CPU] There is a single Intel Xeon E5-2620
\footnote{\url{http://ark.intel.com/products/64594/intel-xeon-processor-e5-2620
-15m-cache-2_00-ghz-7_20-gts-intel-qpi}} fitted. This is a six core processor
with hyper-threading to give twelve hardware threads. The standard clock
frequency is 2GHz with a maximum turbo frequency of 2.5Ghz. There is a total of
15MB ``Intel Smart Cache'' available which acts as Level 3 cache.

\item[RAM] 16GB DDR3 RAM

\item[Intel Xeon Phi] The Intel Xeon Phi is the 51100P
\footnote{\url{http://ark.intel.com/products/71992/intel-xeon-phi-coprocessor-
5110p-8gb-1_053-ghz-60-core}} variant. There are sixty physical CPU cores
running at 1.053GHz, the cores are 4-way hyper-threaded resulting in 240
hardware threads. There is 8GB of on board memory running at 5GT/s for a
theoretical maximum memory bandwidth of 320GB/s. It has been installed in a PCIe
2.0 slot with 16x lane bandwidth giving a total theoretical bandwidth between
its on-board memory and main memory of 8GB/s (500MB/ per lane).

\end{itemize}

\subsection{AMD System}

The system is running the Fedora 18 Linux distribution. This system was used
solely for running the software system on the AMD CPUs and did not have a
graphics card fitted.

\begin{itemize}

\item[CPU] There are four AMD Opteron 6366 HE
\footnote{\url{http://products.amd.com/en-us/OpteronCPUDetail.aspx?id=813&f1=&f2
=&f3=Yes&f4=&f5=&f6=&f7=&f8=&f9=&f10=&f11=&}} (high efficiency) processors
fitted. Each processor has 16 cores running at a base clock speed of 1.8GHz with
a maximum turbo frequency os 3.1GHz. There is 1MB of Level 2 and 16MB of Level 3
Cache available per processor.

\item[RAM] 512GB DDR3 RAM

\end{itemize}

\section{Experiment Setup and Input Files}

12 profiles

Each profile 128MB each

TREC\_ALL.txt - 236MB

collection.raw - pre-parsed TREC\_ALL.txt

bloomfilter.raw (normal, all hits, no hits): 4KB

normal = generated from profile

all hits = 4KB of all 1 bits

no hits = 4KB of all 0 bits

Multiple repetitions

\section{Scoring Only Results}

Scoring only results. Results averaged over the 12 profiles after 10 repetitions
each. The only exception to this was the AMD CPU system where the higher
throughput made 100 repetitions necessary to achieve reliable results.

\begin{tabular}{|l|l|l|l|}
\hline
Device & Test & Time (ms) & Throughput (MB/s)\\
\hline
\multirow{4}{*}{2x Intel Xeon E5462 C++ Single Threaded}
& No Bloom Filter & 2537 & 93 \\
& Bloom Filter & 2617 & 90.2 \\
& Bloom Filter All Hits & 4023 & 58.7 \\
& Bloom Filter No Hits & 2006 & 117.4 \\
\hline
\multirow{4}{*}{2x Intel Xeon E5462 C++ Multi-threaded}
& No Bloom Filter & 390 & 605.1 \\
& Bloom Filter & 336 & 702.4 \\
& Bloom Filter All Hits & 550 & 429.1 \\
& Bloom Filter No Hits & 257 & 918.3 \\
\hline
\multirow{4}{*}{2x Intel Xeon E5462 OpenCL}
& No Bloom Filter & 222 & 1063.1 \\
& Bloom Filter & 156 & 1512.8 \\
& Bloom Filter All Hits & 298 & 791.9 \\
& Bloom Filter No Hits & 104 & 2269.2 \\
\hline
\multirow{4}{*}{nVidia Tesla C2075}
& No Bloom Filter & 258 & 914.7 \\
& Bloom Filter & 232 & 1017.2 \\
& Bloom Filter All Hits & 294 & 802.7 \\
& Bloom Filter No Hits & 216 & 1092.6 \\
\hline
\multirow{4}{*}{Intel Xeon Phi}
& No Bloom Filter & 381 & 619.4 \\
& Bloom Filter & 409 & 577 \\
& Bloom Filter All Hits & 456 & 517.5 \\
& Bloom Filter No Hits & 402 & 587.1 \\
\hline
\multirow{4}{*}{4x AMD Opteron 6366 HE}
& No Bloom Filter & 87 & 2712.6 \\
& Bloom Filter & 50 & 4720 \\
& Bloom Filter All Hits & 96 & 2458.3 \\
& Bloom Filter No Hits & 39 & 6051.3 \\
\hline
\end{tabular}

\section{Parsing and Scoring Results}

Parsing and scoring results. Results averaged over the 12 profiles after 10
repetitions each. Exceptions to this are the CPU+GPU where No Bloom Filter
conducts 20 repetitions, Bloom Filter and Bloom Filter No Hits 23 repetitions,
and Bloom Filter No Hits 22 repetitions.

\begin{tabular}{|l|l|l|l|}
\hline
Device & Test & Time (ms) & Throughput (MB/s)\\
\hline
\multirow{4}{*}{2x Intel Xeon E5462}
& No Bloom Filter & 699 & 337.6 \\
& Bloom Filter & 648 & 364.2 \\
& Bloom Filter All Hits & 782 & 301.8 \\
& Bloom Filter No Hits & 590 & 400 \\
\hline
\multirow{4}{*}{nVidia Tesla C2075}
& No Bloom Filter & 649 & 363.6 \\
& Bloom Filter & 800 & 295 \\
& Bloom Filter All Hits & 876 & 269.4 \\
& Bloom Filter No Hits & 756 & 312.2 \\
\hline
\multirow{4}{*}{2x Intel Xeon E5462 \& nVidia Tesla C2075}
& No Bloom Filter & 386 & 611.4 \\
& Bloom Filter & 401 & 588.5 \\
& Bloom Filter All Hits & 455 & 518.7 \\
& Bloom Filter No Hits & 379 & 622.7 \\
\hline
\multirow{4}{*}{Intel Xeon Phi}
& No Bloom Filter & 499 & 472.9 \\
& Bloom Filter & 514 & 459.1 \\
& Bloom Filter All Hits & 568 & 415.5 \\
& Bloom Filter No Hits & 524 & 450.4 \\
\hline
\multirow{4}{*}{4x AMD Opteron 6366 HE}
& No Bloom Filter & 239 & 987.4 \\
& Bloom Filter & 450 & 524.4 \\
& Bloom Filter All Hits & 474 & 497.9 \\
& Bloom Filter No Hits & 426 & 554 \\
\hline
\end{tabular}

\section{Other Metrics}

\subsection{Performance per Watt}

\subsection{Performance per Dollar}
